The PAPER-32 power spectrum measured at several redshifts

### 2014-03-27 ms.tex
Adding updated pspec vs z figures.

%delay transform, covariance projection (lossless, and lossy), bin and bootstrap average,
\subsection{Power Spectrum}

\section{Discusion}

\begin{figure}
\includegraphics[width=\textwidth]{figures/psa32_pspec_k3pk_vs_z.png}
\caption{Power spectrum amplitude at k=0.3 hMpc$^-1$.  Paciga 2013 GMRT marked with an 'x', Parsons 2013 PAPER limit marked with black, this work marked with blue diamonds.}
\end{figure}

\section{Conclusion}

>>>>

%delay transform, covariance projection (lossless, and lossy), bin and bootstrap average,
\subsection{Power Spectrum}
\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/pspec_Mar24_psa32_zbins_1_80_119_I.png}
\includegraphics[width=0.45\textwidth]{figures/pspec_Mar24_psa32_zbins_1_100_139_I.png}
\includegraphics[width=0.45\textwidth]{figures/pspec_Mar24_psa32_zbins_1_110_149_I.png}
\includegraphics[width=0.45\textwidth]{figures/pspec_Mar24_psa32_zbins_1_119_150_I.png}
\caption{\label{fig:pspecs} Clockwise from top left: power spectra centered on redshifts 8.5, 7.9, 7.6 and 7.5 (frequencies: 149.5, 159.5 164.5, and 167 MHz) at a bandwidth of 20MHz}
\end{figure}
\section{Discusion}

\begin{figure}
\includegraphics[width=\textwidth]{figures/psa_p3k_vs_z_28.png}
\caption{Power spectrum amplitude at k=0.28 hMpc$^-1$.  Paciga 2013 GMRT marked with an 'x', Parsons 2013 PAPER limit marked with thin black, this work marked with thick blue diamonds.}
\end{figure}

\section{Conclusions}
